\textsf{Are large language models superhuman chemists?}

### 2024-10-25 src/tex/acronymns.tex
add note about leaderboard
[showyourwork]
[showyourwork] overleaf sync
more cleanup

\newacronym{llm}{LLM}{large language model}
\newacronym{ml}{ML}{machine learning}
\newacronym{agi}{AGI}{artificial general intelligence}
\newacronym{api}{API}{application programming interface}
\newacronym{mcq}{MCQ}{multiple-choice question}
\newacronym{rest}{REST}{Representational State Transfer}
\newacronym{orm}{ORM}{object relational mapping}
\newacronym{dai}{DAI}{daily allowed intake}
\newacronym{ghs}{GHS}{Globally Harmonized System of Classification and Labelling of Chemicals}
\newacronym{who}{WHO}{World Health Organization}
\newacronym{nmr}{NMR}{nuclear magnetic resonance}
\newacronym{helm}{HELM}{Holistic Evaluation of Language Models}
\newacronym{smiles}{SMILES}{Simplified Molecular Input Line-Entry System}
\newacronym{pca}{PCA}{principal component analysis}
\newacronym{iupac}{IUPAC}{International Union of Pure and Applied Chemistry}

>>>>

\newacronym{llm}{LLM}{large language model}
\newacronym{ml}{ML}{machine learning}
\newacronym{agi}{AGI}{artificial general intelligence}
\newacronym{api}{API}{application programming interface}
\newacronym{mcq}{MCQ}{multiple-choice question}
\newacronym{rest}{REST}{representational state transfer}
\newacronym{orm}{ORM}{object relational mapping}
\newacronym{dai}{DAI}{daily allowed intake}
\newacronym{ghs}{GHS}{globally harmonized system of classification and labelling of chemicals}
\newacronym{who}{WHO}{World Health Organization}
\newacronym{nmr}{NMR}{nuclear magnetic resonance}
\newacronym{helm}{HELM}{Holistic Evaluation of Language Models}
\newacronym{smiles}{SMILES}{simplified molecular input line-entry system}
\newacronym{pca}{PCA}{principal component analysis}
\newacronym{iupac}{IUPAC}{International Union of Pure and Applied Chemistry}
\newacronym{json}{JSON}{JavaScript object notation}
\newacronym{rag}{RAG}{retrieval augmented generation}
\newacronym{ece}{ECE}{expected calibration error}

### 2024-10-25 src/tex/appendix.tex

\begin{figure}[htb]
    \centering
    \includegraphics{figures/overall_performance.pdf}
    \caption{\textbf{Overall performance of the models on the \chembench corpus.} The bar plot shows the fraction of questions that were answered completely correctly by the models. Scores computed on the entire \chembench corpus.}
    \label{fig:barplot_all_correct_all_questions}
    \script{plot_overview_performance_plot.py}
\end{figure}

\Cref{fig:all_questions_models_completely_correct_radar_overall} shows the performance of the models on the different topics of the \chembench corpus.
The general pattern of performance varies significantly between the different topics and is also observed when the models are evaluated on the entire corpus.
However, since some subjects are composed of questions from different sources, the ranking of the models is, in some instances, different from the one on \chembenchmini.

\begin{figure}[htb]
    \centering
    \includegraphics[width=\textwidth]{figures/all_questions_models_completely_correct_radar_overall.pdf}
    \caption{\textbf{Performance of the models on the different topics of the \chembench corpus.} The radar plot shows the performance of the models on the different topics of the \chembench corpus. The performance is measured as the fraction of questions answered completely correctly by the models.
    A score of 1 (full coverage until the outer line of this plot) indicates that all questions were answered completely correctly, while a score of 0 indicates that none were answered completely correctly.
    }
    \label{fig:all_questions_models_completely_correct_radar_overall}
    \script{analyze_model_reports.py}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/performance_per_topic_tiny.pdf}
    \caption{\textbf{Fraction of  correctly answered questions per data source on \chembenchmini.} The heatmap shows, in color, the fraction of questions answered completely correctly by different systems for some of our data sources. The performance is measured as the fraction of questions answered completely correctly by the models. A score of one (red) indicates that all questions were answered completely correctly, while a score of zero (blue) indicates that none were answered completely correctly.
        We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for the leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of signals in an \gls{nmr} spectrum.
    }
    \label{fig:performance_per_topic_tiny}
    \script{analyze_performance_per_source.py}
\end{figure}

@@

In the applications, human participants were presented with molecules as rendered drawings and SMILES strings. \LaTeX\xspace equations and chemical equations were rendered using MathJax (\Cref{fig:screenshots}).

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_score_distribution.pdf}
    \script{plot_human_score_distribution.py}
    \caption{\textbf{Distribution of human scores.} The histogram and kernel density estimates show the fraction of questions answered correctly by the human volunteers.
    Since the best possible score for each question is one and the worst possible score is zero, the values on this plot are between zero and one. A score of one would mean that a volunteer answered all questions correctly. A score of zero would mean that no question was answered correctly.
    We find that the scores for the questions that the human volunteers answered with tools are generally lower than the scores for the questions that the human volunteers answered without tools.
    }
    \label{fig:human_score_distribution}
\end{figure}

We also recorded the time humans took to answer the questions. This time is the time from the question being displayed to the human to the human submitting the answer.

>>>>

\begin{figure}[htb]
    \centering
    \includegraphics{figures/overall_performance.pdf}
    \caption{\textbf{Overall performance of the models on the \chembench corpus.} The bar plot shows the fraction of questions that were answered correctly by the models. Scores computed on the entire \chembench corpus.}
    \label{fig:barplot_all_correct_all_questions}
    \script{plot_overview_performance_plot.py}
\end{figure}

\Cref{fig:all_questions_models_completely_correct_radar_overall} shows the performance of the models on the different topics of the \chembench corpus.
The general pattern of performance varies significantly between the different topics and is also observed when the models are evaluated on the entire corpus.
However, since some subjects are composed of questions from different sources, the ranking of the models is, in some instances, different from the one on the \enquote{tiny} subset.

\begin{table}
    \caption{\textbf{Performance of the models on the \chembench corpus.} The table shows the fraction of questions answered correctly by the models for different skills and difficulty levels.}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_table.tex}
    }
    \label{tab:performance_table}
\end{table}

\begin{table}
    \caption{\textbf{Performance of the models on the \enquote{tiny} subset of the \chembench corpus.} The table shows the fraction of questions answered correctly by the models for different skills and difficulty levels.}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_table_human_subset.tex}
    }
    \label{tab:performance_table_human_subset}
\end{table}

\begin{figure}[htb]
    \centering
    \includegraphics[width=\textwidth]{figures/all_questions_models_completely_correct_radar_overall.pdf}
    \caption{\textbf{Performance of the models on the different topics of the \chembench corpus.} The radar plot shows the performance of the models on the different topics of the \chembench corpus. The performance is measured as the fraction of questions answered correctly by the models.
    A score of 1 indicates that all questions were answered correctly, while a score of 0 indicates that none were answered correctly.
    }
    \label{fig:all_questions_models_completely_correct_radar_overall}
    \script{analyze_model_reports.py}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/performance_per_topic_tiny.pdf}
    \caption{\textbf{Fraction of completely correctly answered questions per data source on the \enquote{tiny} subset.} The heatmap shows, in color, the fraction of questions answered correctly by different systems for some of our data sources. The performance is measured as the fraction of questions answered correctly by the models. A score of one (red) indicates that all questions were answered correctly, while a score of zero (blue) indicates that none were answered correctly.
        We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for the leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of signals in an \gls{nmr} spectrum.
    }
    \label{fig:performance_per_topic_tiny}
    \script{analyze_performance_per_source.py}
\end{figure}

@@

In the applications, human participants were presented with molecules as rendered drawings and SMILES strings. \LaTeX\xspace equations and chemical equations were rendered using MathJax (\Cref{fig:screenshots}).
In the applications, human participants were presented with molecules as rendered drawings and SMILES strings. \LaTeX\xspace equations and chemical equations were rendered using MathJax (\Cref{fig:screenshots}).

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_score_distribution.pdf}
    \script{plot_human_score_distribution.py}
    \caption{\textbf{Distribution of human scores.} The histogram and kernel density estimates show the fraction of questions answered correctly.
    Since the best possible score for each question is one and the worst possible score is zero, the values on this plot are between zero and one.}
    \label{fig:human_score_distribution}
\end{figure}

We also recorded the time humans took to answer the questions (\Cref{fig:human_timing}). This time is the time from the question being displayed to the human to the human submitting the answer.

### 2024-10-25 src/tex/authors.tex
fix some references
feat: cleanup text for submission (#62)

% Question answerers
\credit{Mehrdad Asgari}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Amir~Mohammad~Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Hani~M.~Elbeheiry~}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{María~Victoria~Gil}{0,1,0,0,1,0,0,0,0,0,0,0,0,1}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Caroline T. Holick}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Tim Hoffmann}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Abdelrahman~Ibrahim}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Lea~C.~Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Santiago~Miret}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Jan Matthias Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Nicole Roesner}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Johanna Schreiber}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,1}
\credit{Leanne M. Stafast}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}

@@

\author[1,2,$\star$]{Adrian~Mirza~\orcidlink{0000-0003-4033-4235}}
\author[1,$\star$]{Nawaf~Alampara~\orcidlink{0009-0001-7697-7315}}
\author[1,$\star$]{Sreekanth~Kunchapu~\orcidlink{0009-0003-5752-0154}}
\author[1,2 $\star$]{Martiño~Ríos-García~\orcidlink{0000-0003-1507-4048}}
\author[ ]{Benedict~Emoekabu}
\author[4]{Aswanth~Krishnan~\orcidlink{0009-0008-2703-5613}}
\author[5,6]{Tanya~Gupta~\orcidlink{0009-0001-9523-3290}}
\author[1]{Mara~Wilhelmi~\orcidlink{0009-0007-4392-5918}}
\author[1]{Macjonathan~Okereke~\orcidlink{0009-0007-1013-0502}}

\author[7]{Mehrdad~Asgari~\orcidlink{0000-0002-5427-1610}}
\author[8]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[9]{Amir~Mohammad~Elahi~\orcidlink{0009-0001-5907-101X}}
\author[1]{Hani~M.~Elbeheiry~\orcidlink{0000-0002-5205-2852}}
\author[3]{María~Victoria~Gil~\orcidlink{0000-0003-4894-4660}}
\author[ ]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}
\author[1]{Maximilian~Greiner}
\author[1]{Caroline~T.~Holick~\orcidlink{0009-0000-1724-2725}}
\author[1]{Tim~Hoffmann~\orcidlink{0009-0004-0230-6115}}
\author[1]{Abdelrahman~Ibrahim~\orcidlink{0009-0003-1460-4710}}
\author[1]{Lea~C.~Klepsch~\orcidlink{0009-0009-3849-1670}}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}
\author[10, 11]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Jakob~Meyer}
\author[12]{Santiago~Miret~\orcidlink{0000-0002-4787-2757}}
\author[1]{Jan~Matthias~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}
\author[1, 13]{Nicole~Roesner~\orcidlink{0000-0002-5133-775X}}

\author[1, 11]{Johanna~Schreiber~\orcidlink{0009-0000-0991-8967}}
\author[1,2, 10, 13]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[1, 13]{Leanne~M.~Stafast~\orcidlink{0009-0008-5604-261X}}
\author[14]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}

% Senior authors
\author[15,16]{Michael~Pieler~\orcidlink{0000-0001-9186-7045}}
\author[5, 6]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}
\author[1,2, 10, 13, \Letter]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}

@@

\affil[3]{Institute of Carbon Science and Technology (INCAR), CSIC, Francisco Pintado Fe 26, 33011 Oviedo, Spain}
\affil[4]{QpiVolta Technologies Pvt Ltd}
\affil[5]{Laboratory of Artificial Chemical Intelligence (LIAC), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland}
\affil[6]{National Centre of Competence in Research (NCCR) Catalysis, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland}
\affil[7]{Department of Chemical Engineering \& Biotechnology, University of Cambridge, Philippa Fawcett Drive, Cambridge CB3 0AS, United Kingdom}
\affil[8]{Macromolecular Chemistry, University of Bayreuth, 95447 Bayreuth, Germany}
\affil[9]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Switzerland}
\affil[10]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[11]{Institute for Technical Chemistry and Environmental Chemistry (ITUC), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[12]{Intel Labs}
\affil[13]{Jena Center for Soft Matter (JCSM), Friedrich Schiller University Jena, Philosophenweg 7, 07743 Jena, Germany}

\affil[14]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[15]{OpenBioML.org}
\affil[16]{Stability.AI}

>>>>

% Question answerers
\credit{Anagha Aneesh}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Mehrdad Asgari}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Amir~Mohammad~Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Hani~M.~Elbeheiry~}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{María~Victoria~Gil}{0,1,0,0,1,0,0,0,0,0,0,0,0,1}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Caroline T. Holick}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Tim Hoffmann}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Abdelrahman~Ibrahim}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Lea~C.~Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Santiago~Miret}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Jan Matthias Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Nicole Roesner}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Johanna Schreiber}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,1}
\credit{Leanne M. Stafast}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}

@@

\author[1,2,$\star$]{Adrian~Mirza~\orcidlink{0000-0003-4033-4235}}
\author[1,$\star$]{Nawaf~Alampara~\orcidlink{0009-0001-7697-7315}}
\author[1,$\star$]{Sreekanth~Kunchapu~\orcidlink{0009-0003-5752-0154}}
\author[1,3 $\star$]{Martiño~Ríos-García~\orcidlink{0000-0003-1507-4048}}
\author[ ]{Benedict~Emoekabu}
\author[4]{Aswanth~Krishnan~\orcidlink{0009-0008-2703-5613}}
\author[5,6]{Tanya~Gupta~\orcidlink{0009-0001-9523-3290}}
\author[1]{Mara~Wilhelmi~\orcidlink{0009-0007-4392-5918}}
\author[1]{Macjonathan~Okereke~\orcidlink{0009-0007-1013-0502}}

\author[1]{Anagha~Aneesh~\orcidlink{0009-0001-0275-2586}}
\author[7]{Mehrdad~Asgari~\orcidlink{0000-0002-5427-1610}}
\author[8]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[9]{Amir~Mohammad~Elahi~\orcidlink{0009-0001-5907-101X}}
\author[10]{Hani~M.~Elbeheiry~\orcidlink{0000-0002-5205-2852}}
\author[3]{María~Victoria~Gil~\orcidlink{0000-0003-4894-4660}}
\author[ ]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}
\author[1]{Maximilian~Greiner}
\author[1]{Caroline~T.~Holick~\orcidlink{0009-0000-1724-2725}}
\author[1]{Tim~Hoffmann~\orcidlink{0009-0004-0230-6115}}
\author[1]{Abdelrahman~Ibrahim~\orcidlink{0009-0003-1460-4710}}
\author[1]{Lea~C.~Klepsch~\orcidlink{0009-0009-3849-1670}}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}
\author[11, 12]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Jakob~Meyer}
\author[13]{Santiago~Miret~\orcidlink{0000-0002-4787-2757}}
\author[1]{Jan~Matthias~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1, 14]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}
\author[1, 14]{Nicole~Roesner~\orcidlink{0000-0002-5133-775X}}

\author[1, 14]{Johanna~Schreiber~\orcidlink{0009-0000-0991-8967}}
\author[1,2, 10, 14]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[1, 14]{Leanne~M.~Stafast~\orcidlink{0009-0008-5604-261X}}
\author[15]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}

% Senior authors
\author[16,17]{Michael~Pieler~\orcidlink{0000-0001-9186-7045}}
\author[5, 6]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}
\author[1,2, 11, 14, \Letter]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}

@@

\affil[3]{Institute of Carbon Science and Technology (INCAR), CSIC, Francisco Pintado Fe 26, 33011 Oviedo, Spain}
\affil[4]{QpiVolta Technologies Pvt Ltd}
\affil[5]{Laboratory of Artificial Chemical Intelligence (LIAC), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland}
\affil[6]{National Centre of Competence in Research (NCCR) Catalysis, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland}
\affil[7]{Department of Chemical Engineering \& Biotechnology, University of Cambridge, Philippa Fawcett Drive, Cambridge CB3 0AS, United Kingdom}
\affil[8]{Macromolecular Chemistry, University of Bayreuth, 95447 Bayreuth, Germany}
\affil[9]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Switzerland}
\affil[10]{Institute for Inorganic and Analytical Chemistry (IAAC), Friedrich Schiller University Jena, Humboldtstrasse 8, 07743 Jena, Germany}

\affil[11]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[12]{Institute for Technical Chemistry and Environmental Chemistry (ITUC), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[13]{Intel Labs}
\affil[14]{Jena Center for Soft Matter (JCSM), Friedrich Schiller University Jena, Philosophenweg 7, 07743 Jena, Germany}

\affil[14]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[16]{OpenBioML.org}
\affil[17]{Stability.AI}

### 2024-10-25 src/tex/ms.tex

\begin{figure}
    \includegraphics[width=\textwidth]{figures/overview_figure.pdf}
    \caption{\textbf{Overview of the \chembench framework.} The figure shows the different components of the \chembench framework.
    The framework's foundation is the benchmark corpus that consists of thousands of questions and answers that we manually or semi-automatically compiled from various sources (see \Cref{sec:curation}).
    Questions are classified based on topics, required skills (reasoning, calculation, knowledge, intuition), and difficulty levels.
    We then used this corpus to evaluate the performance of various models and tool-augmented systems using a custom framework. To provide a baseline, we built a web application that we used to survey experts in chemistry.
    The results of the evaluations are then compiled in publicly accessible leaderboards, which we propose as a foundation for evaluating future models.
    }
    \label{fig:overview_figure}
\end{figure}

@@

Notably, we find that models are still limited in their ability to answer knowledge-intensive questions (\Cref{tab:performance_table_human_subset}), that is they did not memorize the relevant facts. Our results indicate that this is not a limitation that could be overcome by simple application of \gls{rag} systems such as \PaperQATwo. This is likely because the required knowledge cannot easily be accessed via papers (which is the only external knowledge \PaperQATwo has access to) but rather by lookup in specialized databases (e.g., PubChem, Gestis), which also the humans in our study used to answer such questions (\Cref{fig:tool_use}).
This indicates that there is still room for improvement of chemical \gls{llm} by training them on more specialized data sources or by integrating them with specialized databases.

In addition, our analysis shows that the performance of models is correlated with their size (see \Cref{fig:model_size_plot}). This is in line with observations in other domains but also indicates that chemical \gls{llm} could, to some extent, be further improved by scaling them up.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\textwidth]{figures/all_questions_models_completely_correct_radar_human.pdf}
    \caption{\textbf{Performance of the models and humans on the different topics on \chembenchmini.} The radar plot shows the performance of the models and humans on the different topics of \chembenchmini. The performance is measured as the fraction of questions that were answered completely correctly by the models.
    The best score for every dimension is one (all questions answered correctly), and the worst is zero (no question answered correctly). A larger colored area indicates a better performance.
    This figure shows the performance on \chembenchmini. The performance of models on the entire corpus is shown in \Cref{fig:performance_per_topic}.
    }
    \label{fig:all_questions_models_completely_correct_radar_human}
    \script{analyze_model_reports.py}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\textwidth]{figures/overview_figure.pdf}
    \caption{\textbf{Overview of the \chembench framework.} The figure shows the different components of the \chembench framework.
    The framework's foundation is the benchmark corpus that consists of thousands of questions and answers that we manually or semi-automatically compiled from various sources (see \Cref{sec:curation}).
    Questions are classified based on topics, required skills (reasoning, calculation, knowledge, intuition), and difficulty levels.
    We then used this corpus to evaluate the performance of various models and tool-augmented systems using a custom framework. To provide a baseline, we built a web application that we used to survey experts in chemistry.
    The results of the evaluations are then compiled in publicly accessible leaderboards (\Cref{sec:leaderboard}), which we propose as a foundation for evaluating future models.
    }
    \label{fig:overview_figure}
\end{figure}

@@

Notably, we find that models are still limited in their ability to answer knowledge-intensive questions (\Cref{tab:performance_table_human_subset}), that is they did not memorize the relevant facts. Our results indicate that this is not a limitation that could be overcome by simple application of \gls{rag} systems such as \PaperQATwo. This is likely because the required knowledge cannot easily be accessed via papers (which is the only external knowledge \PaperQATwo has access to) but rather by lookup in specialized databases (e.g., PubChem, Gestis), which also the humans in our study used to answer such questions (\Cref{fig:tool_use}).
This indicates that there is still room for improvement in chemical \glspl{llm} by training them on more specialized data sources or by integrating them with specialized databases.

In addition, our analysis shows that the performance of models is correlated with their size (see \Cref{fig:model_size_plot}). This is in line with observations in other domains but also indicates that chemical \glspl{llm} could, to some extent, be further improved by scaling them up.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=\textwidth]{figures/all_questions_models_completely_correct_radar_human.pdf}
    \caption{\textbf{Performance of the models and humans on the different topics of the \enquote{tiny} subset of the \chembench corpus.} The radar plot shows the performance of the models and humans on the different topics of \enquote{tiny} subset of the \chembench corpus. The performance is measured as the fraction of questions that were answered correctly by the models.
    The best score for every dimension is one (all questions answered correctly), and the worst is zero (no question answered correctly). A larger colored area indicates a better performance.
    This figure shows the performance on the subset of questions that were answered by humans. The performance of models on the entire corpus is shown in \Cref{fig:barplot_all_correct_all_questions}.
    }
    \label{fig:all_questions_models_completely_correct_radar_human}
    \script{analyze_model_reports.py}
\end{figure}
